Comparing belief in free will and job satisfaction in the US and Taiwan 

### 2024-02-14 paper/paper.qmd
Update paper.qmd

>>>>

"Site Survey Shows 60 Percent Think Free Will Exists; Read Why." *Scientific American Blog Network*, Scientific American, [February 12, 2024]. https://blogs.scientificamerican.com/talking-back/site-survey-shows-60-percent-think-free-will-exists-read-why/.

"Where Belief in Free Will Is Linked to Happiness." *Frontiers in News*, Frontiers, 24 January 2017, https://www.frontiersin.org/news/2017/01/24/where-belief-in-free-will-is-linked-to-happiness/.

"Table 1 Police-reported cybercrime, by type of violation, Canada, provinces and territories." *Statistics Canada*, Government of Canada, [Access Date], https://www150.statcan.gc.ca/t1/tbl1/en/tv.action?pid=4510008801.

"Annual Report to Parliament on Immigration 2023." *Immigration, Refugees and Citizenship Canada*, Government of Canada, 2023, https://www.canada.ca/en/immigration-refugees-citizenship/corporate/publications-manuals/annual-report-parliament-immigration-2023.html#.

Lavazza, Andrea, and Inglese, S. "Free Will and Neuroscience: From Explaining Freedom Away to New Ways of Operationalizing and Measuring It." Frontiers in Psychology, vol. 11, 2020, www.frontiersin.org/articles/10.3389/fpsyg.2020.00120/full. Accessed 14 Feb. 2024.

Wagner, H. "Why We Have Free Will." Scientific American, 6 Jan. 2016, www.scientificamerican.com/article/why-we-have-free-will/. Accessed 14 Feb. 2024.

Ghose, Tia. "Is Free Will an Illusion? Scientists, Philosophers Forced to Differ." Live Science, 3 May 2013, www.livescience.com/29100-illusion-of-free-will.html. Accessed 14 Feb. 2024.
